Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-31 paper2.tex
cleaning up appendix mention

\begin{abstract}
We report modelling follow-up of recently-discovered
gravitational-lens candidates in the Canada France Hawaii Telescope
Legacy Survey. Lens modelling was done by a small group of
specially-interested volunteers from the \SW\ citizen-science community
who originally found the candidate lenses.  Models are categorised
according to seven diagnostics indicating (a)~the image morphology and
how clear or indistinct it is, (b)~whether the mass map and synthetic
lensed image appear to be plausible, and (c)~how the lens-model mass
compares with compares with the abundance-matched halo mass derived
from photometry of the lensing galaxy.
The lens-model masses range from $\sim10^{11}M_\odot$ to
$>10^{13}M_\odot$.  Preliminary estimates of the stellar masses show
(with two outliers) a smaller spread in stellar mass: a factor of a
few below or above $\sim10^{11}M_\odot$.  That is, the stellar-mass
fraction declines sharply as lensing mass increases.  The highest-mass
system with a convincing model is J1434+522 (\sw{05}).  The two low-mass
outliers are J0206-095 (\sw{19}) and J2217+015 (\sw{42}); if these two are
indeed lenses, they are probing an interesting regime of very low
star-formation efficiency.
Some improvements to the modelling software used (SpaghettiLens), and
discussion of strategies for scaling to future surveys with more and
frequent discoveries, are also included.
\end{abstract}

>>>>

\begin{abstract}
We report modelling follow-up of recently-discovered
gravitational-lens candidates in the Canada France Hawaii Telescope
Legacy Survey. Lens modelling was done by a small group of
specially-interested volunteers from the \SW citizen-science community
who originally found the candidate lenses.  Models are categorised
according to seven diagnostics indicating (a)~the image morphology and
how clear or indistinct it is, (b)~whether the mass map and synthetic
lensed image appear to be plausible, and (c)~how the lens-model mass
compares with compares with the abundance-matched halo mass derived
from photometry of the lensing galaxy.
The lens-model masses range from $\sim10^{11}M_\odot$ to
$>10^{13}M_\odot$.  Preliminary estimates of the stellar masses show
(with two outliers) a smaller spread in stellar mass: a factor of a
few below or above $\sim10^{11}M_\odot$.  That is, the stellar-mass
fraction declines sharply as lensing mass increases.  The highest-mass
system with a convincing model is J1434+522 (\sw{05}).  The two low-mass
outliers are J0206-095 (\sw{19}) and J2217+015 (\sw{42}); if these two are
indeed lenses, they are probing an interesting regime of very low
star-formation efficiency.
Some improvements to the modelling software used (SpaghettiLens), and
discussion of strategies for scaling to future surveys with more and
frequent discoveries, are also included.
\end{abstract}

### 2017-08-31 parts/intro.tex
cleaning up appendix mention

This paper is organized as follows:
Section~\ref{sec:candidates_models} introduces the candidates, the models and the diagnostics applied to them.
The following sections elaborate on the diagnostics.
Image morphology diagnostics are explained in Section~\ref{sec:morph} and
diagnostics based on the mass models in Section~\ref{sec:massmodels}.
Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the lensing candidates.
Section~\ref{sec:summary} gives our summary and conclusions.

There are three appendices devoted to various technical issues
relating to modelling.  \cite{2015MNRAS.447.2170K} tested the system
on simulated lenses and identified some areas for improvement.  In
\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass profile to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

The online supplement gives results for all the modelled systems generated
for all the lensing candidates.

@@

While \SW was running, volunteers started working with \SpL to create models of possible lensing candidates found in \SW that were debated on the \SW discussion forums, before they were classified as plausible candidates.
Figure~\ref{fig:time} shows the total number of models generated over time, models created for systems that turned out to be non candidates were not included.
The first beta version of \SpL was launched in May 2013 and additional features were implemented on the fly.
The system was tested by eight major contributors, volunteers that at least generated five models.
In the beginning of August 2013 (day 70) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
A group of five volunteers converged to a set of favourite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
In April 2015 (day 700) the first full version of \SpL was presented for testing.
In the same time the list of identified candidates was made available \citep[as a preprint of the later work][]{2016MNRAS.455.1191M}.
At this stage, the volunteers were asked to complete the sample and to create models for all the lens candidates that were still missing.
The generated models for candidate \sw{29} show that the volunteers converged to a favorable model much faster, after 15 models generated in 30 days.
This modelling effort resulted in a set of 356 \SpL models for all but one of the \SW 59 lens candidates; candidate \sw{39} was not modelled.

@@

Section~\ref{sec:summary} summarises and tabulates the diagnostics in
Table~\ref{tab:models}.

>>>>

This paper is organized as follows:
Section~\ref{sec:candidates_models} introduces the candidates, the models and the diagnostics applied to them.
The following sections elaborate on the diagnostics.
Image morphology diagnostics are explained in Section~\ref{sec:morph} and
diagnostics based on the mass models in Section~\ref{sec:massmodels}.
Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the lensing candidates.
Section~\ref{sec:summary} summarises and tabulates the diagnostics in
Table~\ref{tab:models}.

There are three appendices devoted to various technical issues
relating to modelling.
The online supplement gives results for all the modelled systems generated
for all the lensing candidates.

@@

While \SW was running, volunteers started working with \SpL to create models of possible lensing candidates found in \SW that were debated on the \SW discussion forums, before they were classified as plausible candidates.
Figure~\ref{fig:time} shows the total number of models generated over time, models created for systems that turned out to be non candidates were not included.
The first beta version of \SpL was launched in May 2013 and additional features were implemented on the fly.
The system was tested by eight major contributors, volunteers that at least generated five models.
In the beginning of August 2013 (day 70) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
A group of five volunteers converged to a set of favourite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
In April 2015 (day 700) the first full version of \SpL was presented for testing.
In the same time the list of identified candidates was made available \citep[as a preprint of the later work][]{2016MNRAS.455.1191M}.
At this stage, the volunteers were asked to complete the sample and to create models for all the lens candidates that were still missing.
The generated models for candidate \sw{29} show that the volunteers converged to a favorable model much faster, after 15 models generated in 30 days.
This modelling effort resulted in a set of 377 \SpL models for all but one of the \SW 59 lens candidates; candidate \sw{39} was not modelled.

\cite{2015MNRAS.447.2170K} tested the system
on simulated lenses and identified some areas for improvement.  In
\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass profile to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

@@
